R für die sozioökonomische Forschung

### 2019-10-17 docs/R-SocioEcon-dt.tex
Create book in develop

\begin{verbatim}
#> function (x, k = 1, ...) 
#> {
#>     UseMethod("lead")
#> }
#> <bytecode: 0x7fba5e3fbbb8>
#> <environment: namespace:plm>
\end{verbatim}

@@

\begin{verbatim}
#> function (x, n = 1L, default = NA, order_by = NULL, ...) 
#> {
#>     if (!is.null(order_by)) {
#>         return(with_order(order_by, lead, x, n = n, default = default))
#>     }
#>     if (length(n) != 1 || !is.numeric(n) || n < 0) {
#>         bad_args("n", "must be a nonnegative integer scalar, ", 
#>             "not {friendly_type_of(n)} of length {length(n)}")
#>     }
#>     if (n == 0) 
#>         return(x)
#>     xlen <- length(x)
#>     n <- pmin(n, xlen)
#>     out <- c(x[-seq_len(n)], rep(default, n))
#>     attributes(out) <- attributes(x)
#>     out
#> }
#> <bytecode: 0x7fba6187b268>
#> <environment: namespace:dplyr>
\end{verbatim}

>>>>

\begin{verbatim}
#> function (x, k = 1, ...) 
#> {
#>     UseMethod("lead")
#> }
#> <bytecode: 0x7fc69537cb40>
#> <environment: namespace:plm>
\end{verbatim}

@@

\begin{verbatim}
#> function (x, n = 1L, default = NA, order_by = NULL, ...) 
#> {
#>     if (!is.null(order_by)) {
#>         return(with_order(order_by, lead, x, n = n, default = default))
#>     }
#>     if (length(n) != 1 || !is.numeric(n) || n < 0) {
#>         bad_args("n", "must be a nonnegative integer scalar, ", 
#>             "not {friendly_type_of(n)} of length {length(n)}")
#>     }
#>     if (n == 0) 
#>         return(x)
#>     xlen <- length(x)
#>     n <- pmin(n, xlen)
#>     out <- c(x[-seq_len(n)], rep(default, n))
#>     attributes(out) <- attributes(x)
#>     out
#> }
#> <bytecode: 0x7fc6960e9ea8>
#> <environment: namespace:dplyr>
\end{verbatim}
